Computation and comparison of the stable northeastern United States marine boundary layer

### 2020-12-08 Paper/main.tex
Added comments/caveats about mesh anisoptropy

In addition to these simulations, we also examined the domain and mesh
requirements necessary for the stable offshore boundary layers
considered here.  Based on the calculated turbulent integral
length scale, horizontal domain sizes of 750 m $\times$ 750 m were found
to be necessary for these simulations.  Various mesh resolutions were
also considered for the stable runs, and it was determined that the
finest resolution of $\Delta_x$=2.5 m was able to resolve the longitudinal
length scales and highest temporal frequencies, but inadequate for
resolving the turbulence in the lateral direction.  Further study is
warranted to comprehensively determine the impact of stable
stratification on the required mesh resolution.

>>>>

In addition to these simulations, we also examined the domain and mesh
requirements necessary to capture important physical features of the
stable offshore boundary layers.  Based on the calculated turbulent
integral length scale, horizontal domain sizes of 750 m $\times$ 750 m
were found to be necessary for these simulations.  Various horizontal
mesh resolutions were also considered for the stable runs, and it was
determined that the finest resolution of $\Delta_x$=2.5 m was able to
resolve the longitudinal length scales and highest temporal
frequencies, but inadequate for resolving the turbulence in the
lateral direction.  However, the possible effects of mesh anisotropy
on the one equation turbulence model and the wall function treatment
are not included in this work, and could be important for future
simulations.  We believe that further study is warranted to
comprehensively determine the impact of stable stratification on the
required mesh resolution.
